---
title: "lab_3"
author: "Naomi Liftman"
date: "2023-02-28"
output: pdf_document
---
## Question 1
### Load `similarity_scores.dta` into R, convert into network object. Plot the network (note- start with statnet, then when switching to community detection detach `sna` and `statnet` in a chunk).

```{r message = FALSE, warning = FALSE, error = FALSE}
#load packages
library(rio)
library(statnet)
#load data as a df
sim_as_df <- import("similarity_scores.dta")
#convert to network
sim <-as.network(sim_as_df, mode=c("directed"))
#plot the network
plot.network(sim,label = network.vertex.names(sim))
```

## Question 2
### Tell me the density of the network, number of nodes, level of reciprocity, whether there are any isolates, and whether it is directed.

The density is 0.0221308, there are 50 nodes, the level of reciprocity is 0.8710204, which tells us it is a directed network and there are no isolates. 

```{r}
#summary gives us density and nodes
summary(sim, print.adj=FALSE)
#isolates gives us integer for isolates
isolates(sim, diag=FALSE)
#grecip gives us reciprocity 
grecip(sim)
```

## Question 3
### Conduct a cug-test for reciprocity. Make sure you include a plot and let us know what we can conclude about the level of reciprocity observed in the network. Set the number of simulated networks to 3000.

```{r}
#conduct the test
cug_sim_recp <- cug.test(sim, grecip, reps = 3000)
#print out the test
cug_sim_recp
#give a pretty graph!
plot(cug_sim_recp)
```
We can conclude that the level of reciprocity is much higher than what we would expect for a random network with the same number of nodes. The probability of this level of reciprocity occurring in a random network of the same size is nearly zero. 

## Question 4
### Conduct a cug-test for density, and condition it by the size of the network. Set the number of simulated networks to 1500.

```{r}
cug.test(sim, gden, cmode="size", reps = 1500)
```


## Question 5
### Detach the packages `statnet` and `sna`. Convert the original dataframe into a network object that igraph can use.

```{r}
#detatch statnet and sna
detach(package:statnet)
detach(package:sna)
#load igraph
library(igraph)
```

```{r}
#use data frame to turn into an igraph network object
sim_graph <- graph_from_data_frame(sim_as_df, directed = TRUE)
#silly little plot to make sure it worked
plot(sim_graph)
```


## Question 6
### Estimate the community detection algorithm for walktrap algorithm. Plot the network with community membership included in the graph. How many communities are there?

```{r}
#create the walktrap
walktrap_sim <- cluster_walktrap(sim_graph)
#make a pretty plot
plot(walktrap_sim, sim_graph, edge.width = .5, edge.arrow.size = .2)
#had to make the edges and arrow size smaller or you couldnt see anything
```
There are three clear and distinct communities. 

## Question 7
### Estimate the community detection algorithm for the betweenneess community algorithm. Plot the network with community membership included in the graph. How many communities are there?

```{r}
#build betweeneness algorithm
between_sim <- cluster_edge_betweenness(sim_graph)
#plot it, but difficult to see!
plot(between_sim, sim_graph,edge.width = .5, edge.arrow.size = .2)
#make sure we can see the members to count correctly
membership(between_sim)
```
Based on our graph there appeared to be 8 communities, and we can check this is true using the membership function! So there are 8 communities, but many of them only have themselves. 

## Question 8
### Pick one of the two community detection algorithms, and plot the network as a dendogram.

```{r}
#upload packages
library(dendextend)
library(circlize)
#build denogram and add colors!
sim_den <- as.dendrogram(between_sim) %>% 
  color_branches(k = 8) %>% 
  color_labels(k = 8)
#build a plot of a denogram
plot(sim_den) 
```


## Question 9
### Use the `circlize_dendrogram` to plot the same network as a circle. Don't forget to add colors by community.

```{r}
circlize_dendrogram(sim_den)
```

So pretty!

## Question 10
### Manually change the number of colors to a lower number than the total number of communities in the network. Were you surprise by the communities that merged? Based on your own understanding of states, do you agree with the categories?

```{r}
#build denogram and add colors!
sim_den_wrong <- as.dendrogram(between_sim) %>% 
  color_branches(k = 4) %>% 
  color_labels(k = 4)
#build a plot of a denogram
plot(sim_den_wrong) 
```

I am not super surprised by the communities that they merged. They connected the states that had the closest last connection, and didn't connect the ones with the least connection. This makes sense for AK which is Alaska and HI, which is Hawaii. However, this doesn't really make sense to me for Arizona, as I thought that this was a relatively connected state, unlike Alaska and Hawaii which are not connected to $any$ other states. So I would not agree with that category. 
