---
title: "Lab 1"
author: "Naomi Liftman"
date: "2023-01-26"
output: pdf_document
---

## Question 1 
### Install all required packages, and include a chunk that loads each.

As a heads up, I set all messages, warnings, and errors to FALSE so that this single chunk wouldn't take up 4 pages :).


```{r message = FALSE, warning = FALSE, error = FALSE}
library(ggplot2)
library(devtools)
library(tidyverse)
library(rio)
library(sna)
library(igraph)
library(statnet)
library(UserNetR)
```


## Question 2
### Load the Moreno data and plot the network. In your visualization, change the Vertex size to 3. 

```{r}
friendship <- UserNetR::Moreno

gender <- friendship %v% "gender" 

#change vertex to 3
plot(friendship, vertex.col = gender + 2, vertex.cex = 3)
```


## Question 3
### How many nodes are in the friendship network?

```{r}
network.size(friendship)
```

There are 33 nodes in the friendship network.


## Question 4
### What is the density of the network?

```{r}
gden(friendship)
```

The density of this network is .087, which tells us this network is not very interconnected. 
