---
title: "data!"
author: "Naomi Liftman"
format: pdf
editor: visual
---

# Packages

```{r warning = FALSE, error = FALSE, message = FALSE}
library(incidentally)
library(backbone)
library(smnet)
library(igraph)
library(tidyverse)
library(rio)
library(tidyr)
```

# Scott Code for Cosponsorship of 117th SENATE

```{r warning = FALSE, message = FALSE, error = FALSE}
#pull the 117 senators connections 
B_117_senate <- incidence.from.congress(session = 117, types = c("s", "sres", "sjres", "sconres"), areas = c("All"), format = "igraph")

network_117_senate <- sdsm(B_117_senate, alpha = 0.01, narrative = TRUE)

## Creates matrix object (note adjacency matrix)
el_mat_117_senate <- as_edgelist(network_117_senate)

### creates data frame object
el_117_senate <- as.data.frame(as_edgelist(network_117_senate))
```

# Mutating Cosponsorship of 117th SENATE

```{r}
#remove the senator title from both columns
el_117_senate$V1 <- sub("Sen. ", "", el_117_senate$V1)
el_117_senate$V2 <- sub("Sen. ", "", el_117_senate$V2)

#remove everything after the [
el_117_senate$V1 <- gsub("\\[.*","", el_117_senate$V1)
el_117_senate$V2 <- gsub("\\[.*","", el_117_senate$V2)

#add new columns with the first and last names
el_117_senate$v1_first <- gsub(".*\\, ", "", el_117_senate$V1)   
el_117_senate$v1_last <- gsub("\\,.*","", el_117_senate$V1)
el_117_senate$v2_first <- gsub(".*\\, ", "", el_117_senate$V2)   
el_117_senate$v2_last <- gsub("\\,.*","", el_117_senate$V2) 

#adding them together!
edge_117_senate = el_117_senate %>% 
  unite(v1_full, c(v1_first, v1_last), sep = "", remove = FALSE) %>% 
  unite(v2_full, c(v2_first, v2_last), sep = "", remove = FALSE) %>% 
  select(v1_full, v2_full)
```

# Scott Code for Cosponsorship in 117th HOUSE

```{r warning = FALSE, message = FALSE, error = FALSE}
#pull the 117 senators connections 
B_117_house <- incidence.from.congress(session = 117, types = c("hr", "hres", "hjres", "hconres"), areas = c("All"), format = "igraph")

#this is taking forever to run, not sure why, will check out later
network_117_house <- sdsm(B_117_house, alpha = 0.01, narrative = TRUE)

## Creates matrix object (note adjacency matrix)
el_mat_117_house <- as_edgelist(network_117_house)

### creates data frame object
el_117_house <- as.data.frame(as_edgelist(network_117_house))
```

# Mutating Cosponsorship of 117th HOUSE

```{r}
#remove the house title from both columns
el_117_house$V1 <- sub("Rep. ", "", el_117_house$V1)
el_117_house$V2 <- sub("Rep. ", "", el_117_house$V2)

#remove everything after the [
el_117_house$V1 <- gsub("\\[.*","", el_117_house$V1)
el_117_house$V2 <- gsub("\\[.*","", el_117_house$V2)

#add new columns with the first and last names
el_117_house$v1_first <- gsub(".*\\, ", "", el_117_house$V1)   
el_117_house$v1_last <- gsub("\\,.*","", el_117_house$V1)
el_117_house$v2_first <- gsub(".*\\, ", "", el_117_house$V2)   
el_117_house$v2_last <- gsub("\\,.*","", el_117_house$V2) 

#adding them together!
edge_117_house = el_117_house %>% 
  unite(v1_full, c(v1_first, v1_last), sep = "", remove = FALSE) %>% 
  unite(v2_full, c(v2_first, v2_last), sep = "", remove = FALSE) %>% 
  select(v1_full, v2_full)
```

# MAKING THE FULL EDGE LIST 117th!

```{r}
#full 117th dataframe
full_117_edge <- rbind(edge_117_house, edge_117_senate)

#renaming to get in correct scheme
full_117_edge <- full_117_edge %>% 
  rename("member_i" = 1,
         "member_j" = 2)
```


# RELIGION FOR 117th

```{r}
#importing the df 
religion_117 <- import("/Users/naomiliftman/Desktop/GOV338/Final Project/117congress.xlsx")

#rename the last five names
relig_117 <- religion_117 %>% 
    rename_with(~ tolower(gsub(".", "", .x, fixed = TRUE))) %>%
  rename("type" = 2) %>% 
  rename("name" = 3) %>% 
  rename("party" = 4 ) %>% 
  rename("cont" = 5) %>% 
  rename("religion" = 6)

#rename the state
names(relig_117)[1] = "state"  

#remove the first row
relig_117 <- relig_117[-c(1:1), ]

#only want their name, relig, and party
relig_117 <- relig_117 %>% 
  select("name", "religion", "party")
```

# Fixing religious data for 117th!

```{r}
#having a look at the origional breakdowns
relig_117 %>% 
  group_by(religion) %>% 
  summarize(n = n())

#creating a new 117
rel_117 <- relig_117

#fix all protestant:
rel_117$fix_relig <- ifelse(rel_117$religion == 'Adventist', 'Protestant', rel_117$religion)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Baptist', 'Protestant', rel_117$fix_relig)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Congregationalist', 'Protestant', rel_117$fix_relig)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Episcopalian', 'Protestant', rel_117$fix_relig)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Lutheran', 'Protestant', rel_117$fix_relig)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Methodist', 'Protestant', rel_117$fix_relig)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Pentecostal', 'Protestant', rel_117$fix_relig)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Pietist', 'Protestant', rel_117$fix_relig)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Presbyterian', 'Protestant', rel_117$fix_relig)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Protestant unspecified', 'Protestant', rel_117$fix_relig)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Reformed', 'Protestant', rel_117$fix_relig)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Restorationist', 'Protestant', rel_117$fix_relig)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Unitarian Universalist', 'Protestant', rel_117$fix_relig)

#fix all general catholic
rel_117$fix_relig <- ifelse(rel_117$religion == 'Orthodox', 'Catholic', rel_117$fix_relig)

#fixing all other
rel_117$fix_relig <- ifelse(rel_117$religion == 'Unaffiliated', 'Other', rel_117$fix_relig)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Buddhist', 'Other', rel_117$fix_relig)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Hindu', 'Other', rel_117$fix_relig)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Mormon', 'Other', rel_117$fix_relig)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Muslim', 'Other', rel_117$fix_relig)
rel_117$fix_relig <- ifelse(rel_117$religion == 'Nondenominational', 'Other', rel_117$fix_relig)

#replacing all of the NAs with Unknown along with the dont know
rel_117$fix_relig <- ifelse(rel_117$religion == 'Don\'t know/refused', 'Unknown', rel_117$fix_relig)
rel_117$fix_relig <- rel_117$fix_relig %>% replace_na('Unknown')


rel_117 %>% 
  group_by(fix_relig) %>% 
  summarize(n = n())

rel_117 <- rel_117 %>% 
  select("name", "fix_relig")
```

# Merging the 117th full with the religion!!

```{r}
#now we have something that has the first senators religion
t_117_first <- full_join(rel_117, full_117_edge, by = c("name" = "member_i")) 

#rename so we have a name i and a religion i 
#and only select the i's
t_117_first <- t_117_first %>% 
  rename("religion_i" = "fix_relig",
         "member_i" = "name") %>% 
  select("member_i", "religion_i")

#now we have something that has the second senators religion
t_117_second <- full_join(rel_117, full_117_edge, by = c("name" = "member_j"))

#now we have the name j and religion j 
#and only select the js
t_117_second <- t_117_second %>% 
  rename("religion_j" = "fix_relig",
         "member_j" = "name") %>% 
  select("member_j", "religion_j")

#now we just need them all together!!!
all_117 <- cbind(t_117_first, t_117_second)

#need to make the NAs of the religions but we dont want NAs of the ties
#there were 37662 ties before running this
#THEY are the same!! this is slay
#this is just a gut check we did it correctly
all_117[!is.na(all_117$member_i),]
all_117[!is.na(all_117$member_j),]

#count the number of NAs
sum(is.na(all_117$religion_i))
sum(is.na(all_117$religion_j))

#now we want to make all the NAs be "Unknown
#for i
all_117$religion_i <- all_117$religion_i %>%  
  replace_na("Unknown")

#for j
all_117$religion_j <- all_117$religion_j %>%  
  replace_na("Unknown")
#YAYAYYAYAYAY

#create similarity score!! yay!!
all_117$similarity<- ifelse(all_117$religion_i == all_117$religion_j, 1, 0)

#trying to remove the ones where the member is the same member!! 
#all done!!
all_117 <- all_117[all_117$member_i != all_117$member_j, ]      

#checking number of unknown

```



# Scott Code for Cosponsorship of 112th SENATE

```{r warning = FALSE, message = FALSE, error = FALSE}
#pull the 117 congress connections 
B_112_senate <- incidence.from.congress(session = 112, types = c("s", "sres", "sjres", "sconres"), areas = c("All"), format = "igraph")

network_112_senate <- sdsm(B_112_senate, alpha = 0.01, narrative = TRUE)

## Creates matrix object (note adjacency matrix)
el_mat_112_senate <- as_edgelist(network_112_senate)

### creates data frame object
el_112_senate <- as.data.frame(as_edgelist(network_112_senate))
```

# Mutating Cosponsorship of 112th SENATE

```{r}
#remove the senator title from both columns
el_112_senate$V1 <- sub("Sen. ", "", el_112_senate$V1)
el_112_senate$V2 <- sub("Sen. ", "", el_112_senate$V2)

#remove everything after the [
el_112_senate$V1 <- gsub("\\[.*","", el_112_senate$V1)
el_112_senate$V2 <- gsub("\\[.*","", el_112_senate$V2)

#add new columns with the first and last names
el_112_senate$v1_first <- gsub(".*\\, ", "", el_112_senate$V1)   
el_112_senate$v1_last <- gsub("\\,.*","", el_112_senate$V1)
el_112_senate$v2_first <- gsub(".*\\, ", "", el_112_senate$V2)   
el_112_senate$v2_last <- gsub("\\,.*","", el_112_senate$V2) 

#adding them together!
edge_112_senate = el_112_senate %>% 
  unite(v1_full, c(v1_first, v1_last), sep = "", remove = FALSE) %>% 
  unite(v2_full, c(v2_first, v2_last), sep = "", remove = FALSE) %>% 
  select(v1_full, v2_full)
```

# Scott Code for Cosponsorship in the 112th HOUSE

```{r warning = FALSE, message = FALSE, error = FALSE}
#pull the 117 senators connections 
B_112_house <- incidence.from.congress(session = 112, types = c("hr", "hres", "hjres", "hconres"), areas = c("All"), format = "igraph")

#this is taking forever to run, not sure why, will check out later
network_112_house <- sdsm(B_112_house, alpha = 0.01, narrative = TRUE)

## Creates matrix object (note adjacency matrix)
el_mat_112_house <- as_edgelist(network_112_house)

### creates data frame object
el_112_house <- as.data.frame(as_edgelist(network_112_house))
```

# Mutating Cosponsorship of 112th HOUSE

```{r}
#remove the house title from both columns
el_112_house$V1 <- sub("Rep. ", "", el_112_house$V1)
el_112_house$V2 <- sub("Rep. ", "", el_112_house$V2)

#remove everything after the [
el_112_house$V1 <- gsub("\\[.*","", el_112_house$V1)
el_112_house$V2 <- gsub("\\[.*","", el_112_house$V2)

#add new columns with the first and last names
el_112_house$v1_first <- gsub(".*\\, ", "", el_112_house$V1)   
el_112_house$v1_last <- gsub("\\,.*","", el_112_house$V1)
el_112_house$v2_first <- gsub(".*\\, ", "", el_112_house$V2)   
el_112_house$v2_last <- gsub("\\,.*","", el_112_house$V2) 

#adding them together!
edge_112_house = el_112_house %>% 
  unite(v1_full, c(v1_first, v1_last), sep = "", remove = FALSE) %>% 
  unite(v2_full, c(v2_first, v2_last), sep = "", remove = FALSE) %>% 
  select(v1_full, v2_full)
```

# BUILDING FULL 112th
```{r}
#full 117th dataframe
full_112_edge <- rbind(edge_112_house, edge_112_senate)

#renaming to get in correct scheme
full_112_edge <- full_112_edge %>% 
  rename("member_i" = 1,
         "member_j" = 2)

```


# Religion Data 112th

```{r}
#importing the df 
religion_112 <- import("/Users/naomiliftman/Desktop/GOV338/Final Project/112congress.xlsx") 

#rename the last five names
relig_112 <- religion_112 %>% 
  rename_with(~ tolower(gsub(".", "", .x, fixed = TRUE))) %>% 
  rename("member_name" = 2) %>% 
  rename("religious_affiliation" = 4 ) %>% 
  select("member_name", "religious_affiliation", "party")
```

# Fixing religious data for 112!!

```{r}
#how many religions origionally
relig_112 %>% 
  group_by(religious_affiliation) %>% 
  summarize(n = n())

rel_112 <- relig_112

#fix all other
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Quaker', 'Other', rel_112$religious_affiliation)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Nazarene', 'Other', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Greek Orthodox', 'Other', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Mormon', 'Other', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Buddhist', 'Other', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Muslim', 'Other', rel_112$fix_relig)

#fixing all catholic
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Anglican', 'Catholic', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Anglican Catholic', 'Catholic', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Roman Catholic', 'Catholic', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Unitarian', 'Catholic', rel_112$fix_relig)

#fixing all protestant
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'African Methodist Episcopal', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Evangelical Methodist', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'United Methodist', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Methodist', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Christian', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Christian non-denominational', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Christian Reformed', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Christian Scientist', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Church of Christ', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Antioch Orthodox Christian Church', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Eastern Orthodox', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Evangelical Christian', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Southern Baptist', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Baptist', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Episcopalian', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Presbyterian', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Lutheran', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Lutheran - Missouri Synod', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Evangelical Lutheran', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Seventh-day Adventist', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Community of Christ', 'Protestant', rel_112$fix_relig)
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Congregationalist Baptist', 'Protestant', rel_112$fix_relig)

#replace all NAs with unknown
rel_112$fix_relig <- ifelse(rel_112$religious_affiliation == 'Unspecified', 'Unknown', rel_112$fix_relig)
rel_112$fix_relig <- rel_112$fix_relig %>% replace_na('Unknown')

#how many different religions there are now!
rel_112 %>% 
  group_by(fix_relig) %>% 
  summarize(n = n())

rel_112 <- rel_112 %>% 
  select("member_name", "fix_relig")
```

# Fixing all the Incorrect Missmaches 112!

```{r}
full_112_edge <- full_112_edge %>% 
  mutate(member_i = ifelse(full_112_edge$member_i == "Wm. Lacy Clay", "William Lacy Clay", member_i),
         member_j = ifelse(full_112_edge$member_j == "Wm. Lacy Clay", "William Lacy Clay", member_j),
         member_i = ifelse(full_112_edge$member_i == "W. Todd Akin", "Todd Akin", member_i),
         member_j = ifelse(full_112_edge$member_j == "W. Todd Akin", "Todd Akin", member_j),
         member_i = ifelse(full_112_edge$member_i == "William R. Keating", "William Keating", member_i),
         member_j = ifelse(full_112_edge$member_j == "William R. Keating", "William Keating", member_j),
         member_i = ifelse(full_112_edge$member_i == "William L. Owens", "Bill  Owens", member_i),
         member_j = ifelse(full_112_edge$member_j == "William L. Owens", "Bill  Owens", member_j),
         member_i = ifelse(full_112_edge$member_i == "Thomas E. Petri", "Tom Petri", member_i),
         member_j = ifelse(full_112_edge$member_j == "Thomas E. Petri", "Tom Petri", member_j),
         member_i = ifelse(full_112_edge$member_i == "Theodore E. Deutch", "Ted Deutch", member_i),
         member_j = ifelse(full_112_edge$member_j == "Theodore E. Deutch", "Ted Deutch", member_j),
         member_i = ifelse(full_112_edge$member_i == "Thaddeus G. McCotter", "Thaddeus McCotter", member_i),
         member_j = ifelse(full_112_edge$member_j == "Thaddeus G. McCotter", "Thaddeus McCotter", member_j),
         member_i = ifelse(full_112_edge$member_i == "Susan M. Collins", "Susan Collins", member_i),
         member_j = ifelse(full_112_edge$member_j == "Susan M. Collins", "Susan Collins", member_j),
         member_i = ifelse(full_112_edge$member_i == "Sue Wilkins Myrick", "Sue Myrick", member_i),
         member_j = ifelse(full_112_edge$member_j == "Sue Wilkins Myrick", "Sue Myrick", member_j),
         member_i = ifelse(full_112_edge$member_i == "Steven M. Palazzo", "Steven Palazzo", member_i),
         member_j = ifelse(full_112_edge$member_j == "Steven M. Palazzo", "Steven Palazzo", member_j),
         member_i = ifelse(full_112_edge$member_i == "Steve II Southerland", "Steve Southerland", member_i),
         member_j = ifelse(full_112_edge$member_j == "Steve II Southerland", "Steve Southerland", member_j),
         member_i = ifelse(full_112_edge$member_i == "Stephen Lee Fincher", "Stephen Fincher", member_i),
         member_j = ifelse(full_112_edge$member_j == "Stephen Lee Fincher", "Stephen Fincher", member_j),
         member_i = ifelse(full_112_edge$member_i == "Scott  R. Tipton", "Scott Tipton", member_i),
         member_j = ifelse(full_112_edge$member_j == "Scott  R. Tipton", "Scott Tipton", member_j),
         member_i = ifelse(full_112_edge$member_i == "Rosa L. DeLauro", "Rosa DeLauro", member_i),
         member_j = ifelse(full_112_edge$member_j == "Rosa L. DeLauro", "Rosa DeLauro", member_j),
         member_i = ifelse(full_112_edge$member_i == "Rodney P. Frelinghuysen", "Rodney Frelinghuysen", member_i),
         member_j = ifelse(full_112_edge$member_j == "Rodney P. Frelinghuysen", "Rodney Frelinghuysen", member_j),
         member_i = ifelse(full_112_edge$member_i == "Robert T. Schilling", "Bobby Schilling", member_i),
         member_j = ifelse(full_112_edge$member_j == "Robert T. Schilling", "Bobby Schilling", member_j),
         member_i = ifelse(full_112_edge$member_i == "Robert J. Wittman", "Rob Wittman", member_i),
         member_j = ifelse(full_112_edge$member_j == "Robert J. Wittman", "Rob Wittman", member_j),
         member_i = ifelse(full_112_edge$member_i == "Robert J. Dold", "Robert Dold", member_i),
         member_j = ifelse(full_112_edge$member_j == "Robert J. Dold", "Robert Dold", member_j),
         member_i = ifelse(full_112_edge$member_i == "Robert E. Latta", "Bob Latta", member_i),
         member_j = ifelse(full_112_edge$member_j == "Robert E. Latta", "Bob Latta", member_j),
         member_i = ifelse(full_112_edge$member_i == "Robert C. \"Bobby\" Scott", "Robert C. Scott", member_i),
         member_j = ifelse(full_112_edge$member_j == "Robert C. \"Bobby\" Scott", "Robert C. Scott", member_j),
         member_i = ifelse(full_112_edge$member_i == "Richard L. Hanna", "Richard Hanna", member_i),
         member_j = ifelse(full_112_edge$member_j == "Richard L. Hanna", "Richard Hanna", member_j),
         member_i = ifelse(full_112_edge$member_i == "Richard B. Nugent", "Richard Nugent", member_i),
         member_j = ifelse(full_112_edge$member_j == "Richard B. Nugent", "Richard Nugent", member_j),
         member_i = ifelse(full_112_edge$member_i == "Renee L. Ellmers", "Renee Ellmers", member_i),
         member_j = ifelse(full_112_edge$member_j == "Renee L. Ellmers", "Renee Ellmers", member_j),
         member_i = ifelse(full_112_edge$member_i == "Reid J. Ribble", "Reid Ribble", member_i),
         member_j = ifelse(full_112_edge$member_j == "Reid J. Ribble", "Reid Ribble", member_j),
         member_i = ifelse(full_112_edge$member_i == "Raúl M. Grijalva", "Raul Grijalva", member_i),
         member_j = ifelse(full_112_edge$member_j == "Raúl M. Grijalva", "Raul Grijalva", member_j),
         member_i = ifelse(full_112_edge$member_i == "Peter J. Roskam", "Peter Roskam", member_i),
         member_j = ifelse(full_112_edge$member_j == "Peter J. Roskam", "Peter Roskam", member_j),
         member_i = ifelse(full_112_edge$member_i == "Paul C. Broun", "Paul Broun", member_i),
         member_j = ifelse(full_112_edge$member_j == "Paul C. Broun", "Paul Broun", member_j),
         member_i = ifelse(full_112_edge$member_i == "Paul A. Gosar", "Paul Gosar", member_i),
         member_j = ifelse(full_112_edge$member_j == "Paul A. Gosar", "Paul Gosar", member_j),
         member_i = ifelse(full_112_edge$member_i == "Patrick J. Tiberi", "Pat Tiberi", member_i),
         member_j = ifelse(full_112_edge$member_j == "Patrick J. Tiberi", "Pat Tiberi", member_j),
         member_i = ifelse(full_112_edge$member_i == "Norman D. Dicks", "Norm Dicks", member_i),
         member_j = ifelse(full_112_edge$member_j == "Norman D. Dicks", "Norm Dicks", member_j),
         member_i = ifelse(full_112_edge$member_i == "Nan A. S. Hayworth", "Nan Hayworth", member_i),
         member_j = ifelse(full_112_edge$member_j == "Nan A. S. Hayworth", "Nan Hayworth", member_j),
         member_i = ifelse(full_112_edge$member_i == "Mike J. Rogers", "Mike Rogers", member_i),
         member_j = ifelse(full_112_edge$member_j == "Mike J. Rogers", "Mike Rogers", member_j),
         member_i = ifelse(full_112_edge$member_i == "Michael T. McCaul", "Michael McCaul", member_i),
         member_j = ifelse(full_112_edge$member_j == "Michael T. McCaul", "Michael McCaul", member_j),
         member_i = ifelse(full_112_edge$member_i == "Michael K. Simpson", "Mike Simpson", member_i),
         member_j = ifelse(full_112_edge$member_j == "Michael K. Simpson", "Mike Simpson", member_j),
         member_i = ifelse(full_112_edge$member_i == "Michael G. Grimm", "Michael Grimm", member_i),
         member_j = ifelse(full_112_edge$member_j == "Michael G. Grimm", "Michael Grimm", member_j),
         member_i = ifelse(full_112_edge$member_i == "Michael F. Doyle", "Mike Doyle", member_i),
         member_j = ifelse(full_112_edge$member_j == "Michael F. Doyle", "Mike Doyle", member_j),
         member_i = ifelse(full_112_edge$member_i == "Melvin L. Watt", "Melvin Watt", member_i),
         member_j = ifelse(full_112_edge$member_j == "Melvin L. Watt", "Melvin Watt", member_j),
         member_i = ifelse(full_112_edge$member_i == "Marlin A. Stutzman", "Marlin Stutzman", member_i),
         member_j = ifelse(full_112_edge$member_j == "Marlin A. Stutzman", "Marlin Stutzman", member_j),
         member_i = ifelse(full_112_edge$member_i == "Mark S. Critz", "Mark Critz", member_i),
         member_j = ifelse(full_112_edge$member_j == "Mark S. Critz", "Mark Critz", member_j),
         member_i = ifelse(full_112_edge$member_i == "Lynn C. Woolsey", "Lynn Woolsey", member_i),
         member_j = ifelse(full_112_edge$member_j == "Lynn C. Woolsey", "Lynn Woolsey", member_j),
         member_i = ifelse(full_112_edge$member_i == "Lynn A. Westmoreland", "Lynn Westmoreland", member_i),
         member_j = ifelse(full_112_edge$member_j == "Lynn A. Westmoreland", "Lynn Westmoreland", member_j),
         member_i = ifelse(full_112_edge$member_i == "Louise McIntosh Slaughter", "Louise M. Slaughter", member_i),
         member_j = ifelse(full_112_edge$member_j == "Louise McIntosh Slaughter", "Louise M. Slaughter", member_j),
         member_i = ifelse(full_112_edge$member_i == "Linda T. Sánchez", "Linda T. Sanchez", member_i),
         member_j = ifelse(full_112_edge$member_j == "Linda T. Sánchez", "Linda T. Sanchez", member_j),
         member_i = ifelse(full_112_edge$member_i == "Kristi L. Noem", "Kristi Noem", member_i),
         member_j = ifelse(full_112_edge$member_j == "Kristi L. Noem", "Kristi Noem", member_j),
         member_i = ifelse(full_112_edge$member_i == "Jr. Sensenbrenner", "F. James Sensenbrenner Jr.", member_i),
         member_j = ifelse(full_112_edge$member_j == "Jr. Sensenbrenner", "F. James Sensenbrenner Jr.", member_j),
         member_i = ifelse(full_112_edge$member_i == "Jr. Pascrell", "Bill Pascrell Jr.", member_i),
         member_j = ifelse(full_112_edge$member_j == "Jr. Pascrell", "Bill Pascrell Jr.", member_j),
         member_i = ifelse(full_112_edge$member_i == "Jr. Pallone", "Frank Pallone Jr.", member_i),
         member_j = ifelse(full_112_edge$member_j == "Jr. Pallone", "Frank Pallone Jr.", member_j),
         member_i = ifelse(full_112_edge$member_i == "Jr. Jackson", "Jesse L. Jackson Jr.", member_i),
         member_j = ifelse(full_112_edge$member_j == "Jr. Jackson", "Jesse L. Jackson Jr.", member_j),
         member_i = ifelse(full_112_edge$member_i == "Jr. Duncan", "John J. \"Jimmy\" Duncan Jr.", member_i),
         member_j = ifelse(full_112_edge$member_j == "Jr. Duncan", "John J. \"Jimmy\" Duncan Jr.", member_j),
         member_i = ifelse(full_112_edge$member_i == "Jr. Conyers", "John Conyers Jr.", member_i),
         member_j = ifelse(full_112_edge$member_j == "Jr. Conyers", "John Conyers Jr.", member_j),
         member_i = ifelse(full_112_edge$member_i == "Jr. Carney", "John Carney", member_i),
         member_j = ifelse(full_112_edge$member_j == "Jr. Carney", "John Carney", member_j),
         member_i = ifelse(full_112_edge$member_i == "Jr. Boustany", "Charles Boustany Jr.", member_i),
         member_j = ifelse(full_112_edge$member_j == "Jr. Boustany", "Charles Boustany Jr.", member_j),
         member_i = ifelse(full_112_edge$member_i == "Jr. Bishop", "Sanford D. Bishop Jr.", member_i),
         member_j = ifelse(full_112_edge$member_j == "Jr. Bishop", "Sanford D. Bishop Jr.", member_j),
         member_i = ifelse(full_112_edge$member_i == "Joseph R. Pitts", "Joe Pitts", member_i),
         member_j = ifelse(full_112_edge$member_j == "Joseph R. Pitts", "Joe Pitts", member_j),
         member_i = ifelse(full_112_edge$member_i == "Joseph J. Heck", "Joe Heck", member_i),
         member_j = ifelse(full_112_edge$member_j == "Joseph J. Heck", "Joe Heck", member_j),
         member_i = ifelse(full_112_edge$member_i == "John R. Carter", "John Carter", member_i),
         member_j = ifelse(full_112_edge$member_j == "John R. Carter", "John Carter", member_j),
         member_i = ifelse(full_112_edge$member_i == "John P. Sarbanes", "John Sarbanes", member_i),
         member_j = ifelse(full_112_edge$member_j == "John P. Sarbanes", "John Sarbanes", member_j),
         member_i = ifelse(full_112_edge$member_i == "John Abney Culberson", "John Culberson", member_i),
         member_j = ifelse(full_112_edge$member_j == "John Abney Culberson", "John Culberson", member_j),
         member_i = ifelse(full_112_edge$member_i == "John A. Yarmuth", "John Yarmuth", member_i),
         member_j = ifelse(full_112_edge$member_j == "John A. Yarmuth", "John Yarmuth", member_j),
         member_i = ifelse(full_112_edge$member_i == "Jeffrey M. Landry", "Jeff Landry", member_i),
         member_j = ifelse(full_112_edge$member_j == "Jeffrey M. Landry", "Jeff Landry", member_j),
         member_i = ifelse(full_112_edge$member_i == "Janice D. Schakowsky", "Jan Schakowsky", member_i),
         member_j = ifelse(full_112_edge$member_j == "Janice D. Schakowsky", "Jan Schakowsky", member_j),
         member_i = ifelse(full_112_edge$member_i == "James R. Langevin", "Jim Langevin", member_i),
         member_j = ifelse(full_112_edge$member_j == "James R. Langevin", "Jim Langevin", member_j),
         member_i = ifelse(full_112_edge$member_i == "James P. McGovern", "Jim McGovern", member_i),
         member_j = ifelse(full_112_edge$member_j == "James P. McGovern", "Jim McGovern", member_j),
         member_i = ifelse(full_112_edge$member_i == "James B. Renacci", "Jim Renacci", member_i),
         member_j = ifelse(full_112_edge$member_j == "James B. Renacci", "Jim Renacci", member_j),
         member_i = ifelse(full_112_edge$member_i == "James A. Himes", "Jim Himes", member_i),
         member_j = ifelse(full_112_edge$member_j == "James A. Himes", "Jim Himes", member_j),
         member_i = ifelse(full_112_edge$member_i == "Jaime Herrera Beutler", "Jaime Herrera", member_i),
         member_j = ifelse(full_112_edge$member_j == "Jaime Herrera Beutler", "Jaime Herrera", member_j),
         member_i = ifelse(full_112_edge$member_i == "II Rahall", "Nick J. Rahall II", member_i),
         member_j = ifelse(full_112_edge$member_j == "II Rahall", "Nick J. Rahall II", member_j),
         member_i = ifelse(full_112_edge$member_i == "Henry C. \"Hank,\" Jr. Johnson", "Hank Johnson", member_i),
         member_j = ifelse(full_112_edge$member_j == "Henry C. \"Hank,\" Jr. Johnson", "Hank Johnson", member_j),
         member_i = ifelse(full_112_edge$member_i == "H. Morgan Griffith", "Morgan Griffith", member_i),
         member_j = ifelse(full_112_edge$member_j == "H. Morgan Griffith", "Morgan Griffith", member_j),
         member_i = ifelse(full_112_edge$member_i == "Gus M. Bilirakis", "Gus Bilirakis", member_i),
         member_j = ifelse(full_112_edge$member_j == "Gus M. Bilirakis", "Gus Bilirakis", member_j),
         member_i = ifelse(full_112_edge$member_i == "Gary C. Peters", "Gary Peters", member_i),
         member_j = ifelse(full_112_edge$member_j == "Gary C. Peters", "Gary Peters", member_j),
         member_i = ifelse(full_112_edge$member_i == "G. K. Butterfield", "G.K. Butterfield", member_i),
         member_j = ifelse(full_112_edge$member_j == "G. K. Butterfield", "G.K. Butterfield", member_j),
         member_i = ifelse(full_112_edge$member_i == "Frederica S. Wilson", "Frederica Wilson", member_i),
         member_j = ifelse(full_112_edge$member_j == "Frederica S. Wilson", "Frederica Wilson", member_j),
         member_i = ifelse(full_112_edge$member_i == "Frank C. Guinta", "Frank Guinta", member_i),
         member_j = ifelse(full_112_edge$member_j == "Frank C. Guinta", "Frank Guinta", member_j),
         member_i = ifelse(full_112_edge$member_i == "Fortney Pete Stark", "Pete Stark", member_i),
         member_j = ifelse(full_112_edge$member_j == "Fortney Pete Stark", "Pete Stark", member_j),
         member_i = ifelse(full_112_edge$member_i == "Eric A. \"Rick\" Crawford", "Rick Crawford", member_i),
         member_j = ifelse(full_112_edge$member_j == "Eric A. \"Rick\" Crawford", "Rick Crawford", member_j),
         member_i = ifelse(full_112_edge$member_i == "E. Scott Rigell", "Scott Rigell", member_i),
         member_j = ifelse(full_112_edge$member_j == "E. Scott Rigell", "Scott Rigell", member_j),
         member_i = ifelse(full_112_edge$member_i == "Duncan D. Hunter", "Duncan Hunter", member_i),
         member_j = ifelse(full_112_edge$member_j == "Duncan D. Hunter", "Duncan Hunter", member_j),
         member_i = ifelse(full_112_edge$member_i == "Doris O. Matsui", "Doris Matsui", member_i),
         member_j = ifelse(full_112_edge$member_j == "Doris O. Matsui", "Doris Matsui", member_j),
         member_i = ifelse(full_112_edge$member_i == "Donna F. Edwards", "Donna Edwards", member_i),
         member_j = ifelse(full_112_edge$member_j == "Donna F. Edwards", "Donna Edwards", member_j),
         member_i = ifelse(full_112_edge$member_i == "Donald A. Manzullo", "Donald Manzullo", member_i),
         member_j = ifelse(full_112_edge$member_j == "Donald A. Manzullo", "Donald Manzullo", member_j),
         member_i = ifelse(full_112_edge$member_i == "Dennis A. Ross", "Dennis Ross", member_i),
         member_j = ifelse(full_112_edge$member_j == "Dennis A. Ross", "Dennis Ross", member_j),
         member_i = ifelse(full_112_edge$member_i == "Dennis A. Cardoza", "Dennis Cardoza", member_i),
         member_j = ifelse(full_112_edge$member_j == "Dennis A. Cardoza", "Dennis Cardoza", member_j),
         member_i = ifelse(full_112_edge$member_i == "David N. Cicilline", "David Cicilline", member_i),
         member_j = ifelse(full_112_edge$member_j == "David N. Cicilline", "David Cicilline", member_j),
         member_i = ifelse(full_112_edge$member_i == "David P. Roe", "Phil Roe", member_i),
         member_j = ifelse(full_112_edge$member_j == "David P. Roe", "Phil Roe", member_j),
         member_i = ifelse(full_112_edge$member_i == "David G. Reichert", "Dave Reichert", member_i),
         member_j = ifelse(full_112_edge$member_j == "David G. Reichert", "Dave Reichert", member_j),
         member_i = ifelse(full_112_edge$member_i == "David B. McKinley", "David McKinley", member_i),
         member_j = ifelse(full_112_edge$member_j == "David B. McKinley", "David McKinley", member_j),
         member_i = ifelse(full_112_edge$member_i == "Darrell E. Issa", "Darrell Issa", member_i),
         member_j = ifelse(full_112_edge$member_j == "Darrell E. Issa", "Darrell Issa", member_j),
         member_i = ifelse(full_112_edge$member_i == "Daniel E. Lungren", "Dan Lungren", member_i),
         member_j = ifelse(full_112_edge$member_j == "Daniel E. Lungren", "Dan Lungren", member_j),
         member_i = ifelse(full_112_edge$member_i == "Colleen W. Hanabusa", "Colleen Hanabusa", member_i),
         member_j = ifelse(full_112_edge$member_j == "Colleen W. Hanabusa", "Colleen Hanabusa", member_j),
         member_i = ifelse(full_112_edge$member_i == "Christopher P. Gibson", "Chris Gibson", member_i),
         member_j = ifelse(full_112_edge$member_j == "Christopher P. Gibson", "Chris Gibson", member_j),
         member_i = ifelse(full_112_edge$member_i == "Charles W. Dent", "Charlie Dent", member_i),
         member_j = ifelse(full_112_edge$member_j == "Charles W. Dent", "Charlie Dent", member_j),
         member_i = ifelse(full_112_edge$member_i == "Charles J. \"Chuck\" Fleischmann", "Chuck Fleischmann", member_i),
         member_j = ifelse(full_112_edge$member_j == "Charles J. \"Chuck\" Fleischmann", "Chuck Fleischmann", member_j),
         member_i = ifelse(full_112_edge$member_i == "Charles F. Bass", "Charles Bass", member_i),
         member_j = ifelse(full_112_edge$member_j == "Charles F. Bass", "Charles Bass", member_j),
         member_i = ifelse(full_112_edge$member_i == "Cedric L. Richmond", "Cedric Richmond", member_i),
         member_j = ifelse(full_112_edge$member_j == "Cedric L. Richmond", "Cedric Richmond", member_j),
         member_i = ifelse(full_112_edge$member_i == "C. W. Bill Young", "C.W. Bill Young", member_i),
         member_j = ifelse(full_112_edge$member_j == "C. W. Bill Young", "C.W. Bill Young", member_j),
         member_i = ifelse(full_112_edge$member_i == "C. A. Dutch Ruppersberger", "C.A. Dutch Ruppersberger", member_i),
         member_j = ifelse(full_112_edge$member_j == "C. A. Dutch Ruppersberger", "C.A. Dutch Ruppersberger", member_j),
         member_i = ifelse(full_112_edge$member_i == "Bruce L. Braley", "Bruce Braley", member_i),
         member_j = ifelse(full_112_edge$member_j == "Bruce L. Braley", "Bruce Braley", member_j),
         member_i = ifelse(full_112_edge$member_i == "Bennie G. Thompson", "Bennie Thompson", member_i),
         member_j = ifelse(full_112_edge$member_j == "Bennie G. Thompson", "Bennie Thompson", member_j),
         member_i = ifelse(full_112_edge$member_i == "Allen B. West", "Allen West", member_i),
         member_j = ifelse(full_112_edge$member_j == "Allen B. West", "Allen West", member_j),
         member_i = ifelse(full_112_edge$member_i == "Charles A. Gonzalez", "Charlie Gonzalez", member_i),
         member_j = ifelse(full_112_edge$member_j == "Charles A. Gonzalez", "Charlie Gonzalez", member_j),
         member_i = ifelse(full_112_edge$member_i == "Timothy J. Walz", "Tim Walz", member_i),
         member_j = ifelse(full_112_edge$member_j == "Timothy J. Walz", "Tim Walz", member_j),
         member_i = ifelse(full_112_edge$member_i == "Christopher J. Lee", "Christopher Lee", member_i),
         member_j = ifelse(full_112_edge$member_j == "Christopher J. Lee", "Christopher Lee", member_j),
         member_i = ifelse(full_112_edge$member_i == "III Manchin", "Joe Manchin III", member_i),
         member_j = ifelse(full_112_edge$member_j == "III Manchin", "Joe Manchin III", member_j),
         member_i = ifelse(full_112_edge$member_i == "", "", member_i),
         member_j = ifelse(full_112_edge$member_j == "", "", member_j))
```


# Merging the 112th full with the religion!!

```{r}
#now we have something that has the first senators religion
t_112_first <- full_join(rel_112, full_112_edge, by = c("member_name" = "member_i")) 

#remove all the NAs that were created
t_112_first <- t_112_first %>% 
  drop_na(member_j)

#rename so we have a name i and a religion i 
#and only select the i's
t_112_first <- t_112_first %>% 
  rename("religion_i" = "fix_relig",
         "member_i" = "member_name") %>% 
  select("member_i", "religion_i")

#now we have something that has the second senators religion
t_112_second <- full_join(rel_112, full_112_edge, by = c("member_name" = "member_j"))

#remove all the NAs that were created
t_112_second <- t_112_second %>% 
  drop_na(member_i)

#now we have the name j and religion j 
#and only select the js
t_112_second <- t_112_second %>% 
  rename("religion_j" = "fix_relig",
         "member_j" = "member_name") %>% 
  select("member_j", "religion_j")

#now we just need them all together!!!
all_112 <- cbind(t_112_first, t_112_second)

#count the number of NAs
sum(is.na(all_112$religion_i))
sum(is.na(all_112$religion_j))

#now we want to make all the NAs be "Unknown"
#for i
all_112$religion_i <- all_112$religion_i %>%  
  replace_na("Unknown")

#for j
all_112$religion_j <- all_112$religion_j %>%  
  replace_na("Unknown")
#YAYAYYAYAYAY

#create similarity score!! yay!!
all_112$similarity<- ifelse(all_112$religion_i == all_112$religion_j, 1, 0)

#trying to remove the ones where the member is the same member!! 
#all done!!
all_112 <- all_112[all_112$member_i != all_112$member_j, ]   

#check how many unknowns we got
#remove all the duplicates and check the number of unknowns
all_112 %>% 
  distinct(member_i, .keep_all = TRUE) %>% 
  group_by(religion_j) %>% 
  summarize(n = n())
#currently missing 4 
```
# Summary Statistics of 112
```{r}
all_112 %>% 
  group_by(member_i) %>% 
  summarize(mean = mean())
  
spons_112 <- data.frame(table(all_112$member_j))

cospons_112 <- data.frame(table(all_112$member_i))

spons_112 %>% 
  summarize(mean = mean(Freq),
            sd = sd(Freq))

cospons_112 %>% 
  summarize(mean = mean(Freq),
            sd = sd(Freq))
```





# NOW THAT WE HAVE THE EDGE LISTS we need to make a MATRIX of 112
```{r}
#now we just want the member names
a_112 <- all_112 %>% 
  select(member_i, member_j)

#convert to a network
net_112 <- graph.data.frame(a_112, directed=T)
#convert to a matrix
#now we are seeing that Juniors got recked in this, there are some that we are just going to have to hand do 
mat_112 <- as.matrix(get.adjacency(net_112))
```





# fucking about
```{r}
#making a number correlation for each lmao
rel_112 <- rel_112 %>% 
  mutate(fix_relig = ifelse(rel_112$fix_relig == "Catholic", 1, fix_relig),
         fix_relig = ifelse(rel_112$fix_relig == "Jewish", 2, fix_relig),
         fix_relig = ifelse(rel_112$fix_relig == "Other", 3, fix_relig),
         fix_relig = ifelse(rel_112$fix_relig == "Protestant", 4, fix_relig),
         fix_relig = ifelse(rel_112$fix_relig == "Unknown", 5, fix_relig))  

#trying to figure out all the messed up members and fixing them
s_112 <- all_112 %>% 
  distinct(member_i, .keep_all = TRUE) %>% 
  group_by(religion_i) %>% 
  summarize(n = n())

```
