---
title: "3/7 In Class Work"
author: "Naomi Liftman"
date: "2023-03-07"
output: pdf_document
---
## Load packages and data

```{r, warning=F, message=F, echo=F}
library(rio)
library(statnet)
```


```{r}

# Independent variables
census <- as.matrix(import("censusreg_mat.csv")) #same census region
latent <- as.matrix(import("latent_mat.csv")) # latent tie
culture <- as.matrix(import("culture_mat.csv")) # same cultural region
distance <- as.matrix(import("distance_mat.csv")) # distance between state capitols- standardized

### DV- similarity
similarity <- as.matrix(import("sim_mat.csv"))
```


## For transitivity- convert latent network to network object
```{r}
latent_net <- as.network(latent, directed = TRUE)
```

```{r}
gtrans(latent_net)
#figure out what percent of triad have transitive connections
#is this high or low?
triad.census(latent_net)
#code matches the table from earlier
```

Want to test if more or less transitivity using cug test conditional on something, and to see if the observed transitivity is what we expect.

### Notice how our conclusions change based on what we condition.

```{r}
cug_trans <- cug.test(latent_net,gtrans,cmode="edges")
#edges
plot(cug_trans)
```

Condition based on edges!

```{r}
cug_trans1 <- cug.test(latent_net,gtrans,cmode="size")
#size
plot(cug_trans1)

```

Condition based on size!

```{r}
cug_trans2 <- cug.test(latent_net,gtrans,cmode="dyad.census")
#dyad cencus
plot(cug_trans2)
```

Condition based on dyad census, which tells us if it is a reciprocated, no tie, or a single tie between nodes. 

## Plot network

```{r}
## Very ugly
plot(latent_net)
```

There are a lot of ties, so it's going to be a challenge to visualize.

```{r}
deg <- degree(latent_net)
plot(latent_net, label = network.vertex.names(latent_net), vertex.cex=deg/10)
```

# Network regression- stacking matrices

```{r}
### Stacking IVs into 3 dimensional matrix
#four for the number of variables, and length needs to be the size of one of the matrices
#all matrices should be the same dimensions
state_matrices <- array(NA, c(4, length(census[1,]),length(census[1,]))) 

#independent variable one is cencus region
state_matrices[1,,] <- census
#same for latent
state_matrices[2,,] <- latent
#same for culture
state_matrices[3,,] <- culture
#final for distance
state_matrices[4,,] <- distance

### Now the Linear Model
### can specify number of simulations
### F-stat tells us if the model significant predicts ties
### P<B gives us the p-value  for the probability of observing our coefficient if the true population parameter is not-negative
### P<B gives us the p-value  for the probability of observing our coefficient if the true population parameter is not-positive
### P<B gives us the p-value  for the probability of observing our coefficient if the true population parameter is not zero


```

## Estimating model- assigning coefficient names

```{r}
#network lm
#similarity is the dependent and the array is the independent variables
state_sim_lm<-netlm(similarity, state_matrices, reps=100)

#lets label the variables! 
#create a new list thats a summary of the model and label each of the variables
state_model <- list()
state_model <- summary(state_sim_lm)
#need to make sure you label in the order you read them into R
state_model$names <- c("Intercept", "Same Census Region", "Latent Tie", "Shared Culture", "Distance")

#round the coefficients so that they are not too bad 
state_model$coefficients = round(state_model$coefficients, 2)
state_model
```

## Print results

```{r}
state_model
```

The similarity score increases by .07 for states that belong to the same census region. 
The similarity score decreases by .02 for each 100 mile increase in states. 

## Same thing with binary outcome- logistic regression
Logistic regression because we have a binary variable
Tie-latent connection
```{r}
## IF DV is binary, ca do netlogit model
### Let's change DV to a model of latent nets

latent_matrices <- array(NA, c(4, length(census[1,]),length(census[1,]))) 

latent_matrices[1,,] <- census
latent_matrices[2,,] <- similarity
latent_matrices[3,,] <- culture
latent_matrices[4,,] <- distance


#use netlogit instead of netlm
latent_lm<-netlogit(latent, latent_matrices, reps=100)

latent_model <- list()
latent_model <- summary(latent_lm)
latent_model$names <- c("Intercept", "Same Census Region", "Similarity Score", "Shared Culture", "Distance")

```


## Print results

```{r}
latent_model
```
Interesting!! Cool

Can we conclude that these factors predict latent ties or not?
Similarity score is statistically significant, it is less than .05. So it increases by 2.29
